Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-07-02 template.tex
pushing hard to the finish line (of theory bit)

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\usepackage{verbatim}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

@@

%\item The behavior of the RLC oscillator can be extended to the charging state, and the decaying state, via the time-reversal of Eq. \ref{eq:r}.  Times with $t\leq 0$ correspond to the charging state, $t=0$ corresponds to peak response, and $t\geq 0$ corresponds to the decaying state.  For the charging state:
%\begin{align}
%r(t) &= R_0 e^{2 \pi \gamma_r t} \cos(2\pi f_0 t) \label{eq:rc} \\
%r_a(t) &= R_0 e^{2 \pi \gamma_r t} e^{2\pi j f_0 t} \label{eq:rac}
%\end{align}
%The resonance frequency remains the same as the decaying state, and $\gamma_r$ corresponds to the \textit{rise time} in the same way that $\gamma_f$ corresponds to the \textit{fall time.}  In general, the rise and fall times do not have to be equal.

@@

The integral is the Laplace transform of the shifted Dawson function, with respect to $k$.  Let $v = u-x$, so that

@@

k\int_{0}^{\infty} e^{-ku} D(u-x) du = \\ k e^{-kx} \left( \mathcal{L}\lbrace D(v) \rbrace_k - \int_0^{x} e^{kv} D(v) dv\right)

@@

\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$:
r_a(t) * s_a(t) = \\
\sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) - j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} + \\
j\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + j\sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:final}
The units of convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq. \ref{eq:final} has these units.  The first term is proportional to $R_0 \sigma_t s(t)$, and $s(t)$ has units of $E_0 \sigma_t$, so the unit product is $R_0 E_0\sigma_t^2$.  The units of the second term are $R_0 E_0\sigma_t^2$.  The third term has units of $E_0\sigma_t^2 r_a(t)$, and $r_a(t)$ has units of $R_0$, so the unit product is $R_0 E_0\sigma_t^2$.  The fourth term has units of $R_0 \sigma_t s(t)$, like the first term.  Thus, all units check.  To check the limits, the parameters within $z$ and $z_1$ must be recalled.  Combining prior definitions, the results are
z &= \sqrt{2}\sigma_t \pi f_0 + j\left(\frac{\sigma_t\gamma}{\sqrt{2}} - x\right) \\
z_1 &= f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)
Recall that $\sigma_t = 1/(2\pi \sigma_f)$, and $x=t/(\sqrt{2}\sigma_t)$.  Substituting this into the definition of $z$ reveals that

@@

z_1 = z + jx

@@

Thus, when $t=0$, the two poles are equal, since $t=0$ means $x=0$.  Taking the magnitude of Eq. \ref{eq:final}, and multiplying by $1/2$, gives the final result:

@@

\item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain.  Starting with the definitions of $s(t)$, $r(t)$, and the convolution integral:

@@

s * r &= \int_0^{\infty} r(\tau) s(t-\tau) d\tau \\
s * r &= -E_0 \int_0^{\infty} r(\tau) (t-\tau) e^{-\frac{1}{2}\left(\frac{t-\tau}{\sigma_t}\right)^2}d\tau \\
s * r &= \left(s(t) + E_0 \sigma_t^2 e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dt} \right)I(t,\sigma_t) \label{eq:conv_1} \\
I(t,\sigma_t) &= \int_0^{\infty} r(\tau) e^{(t\tau)/\sigma_t^2} e^{-\frac{1}{2}\left(\frac{\tau}{\sigma_t}\right)^2}d\tau

@@

To compute $I(t,\sigma_t)$, let
z &= \gamma - 2\pi j f_0 \\
z_0 &= \sqrt{2}\sigma_t z\\
x &= t/(\sqrt{2} \sigma_t) \\
y &= \tau/(\sqrt{2} \sigma_t) \\
r(\tau) &= \Re\left\lbrace R_0 e^{-z\tau}\right\rbrace
These substitutions simply $I(t,\sigma_t)$ to
I(t,\sigma_t) = \sqrt{2} \sigma_t R_0 \Re \left\lbrace\int_0^{\infty} e^{(2y-z_0)x} e^{-x^2} dx \right\rbrace
Let $b = y-z_0/2$, Completing the square in the exponent gives
I(t,\sigma_t) = \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\left\lbrace e^{b^2} \erfc(-b) \right\rbrace
Let $b = jc$, so that
I(t,\sigma_t) &= \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\lbrace e^{-c^2} \erfc(-jc) \rbrace \\
I(t,\sigma_t) &= \sqrt{\frac{\pi}{2}} \sigma_t R_0 \Re\lbrace w(c) \rbrace
The Faddeeva function $w(z)$ may be broken into real and imaginary parts using the Voigt functions:
U(p,q) + jV(p,q) = \sqrt{\frac{\pi}{4q}} w(z)
The relationship between $p$, $q$, and $z$ is $z=(1-jp)/(2\sqrt{q})$.  Using this relationship, we find
p &= \left(\frac{t}{\sigma_t}\right)\left(\frac{\sigma_f}{f_0}\right) - \frac{\gamma}{2\pi f_0} \\
q &= \frac{1}{2}\left(\frac{\sigma_f}{f_0}\right)^2
Thus, the integral $I(t,\sigma_t)$ becomes
I(t,\sigma_t) = \sigma_t R_0 \left(\frac{\sigma_f}{f_0}\right) U(p,q)
Substituting the result for $I(t,\sigma_t)$ in Eq. \ref{eq:conv_1} gives
s * r = \\
 R_0\sigma_t \left(\frac{\sigma_f}{f_0}\right) \left(s(t) + E_0 \sigma_t^2 e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dt} \right) U(p,q) \label{eq:conv_2}
Equation \ref{eq:conv_2} can be simplified in two ways.  First, note that $\sigma_t \sigma_f = 1/(2\pi)$, so $R_0\sigma_t (\sigma_f/f_0) = R_0/(2\pi f_0)$.  Second, the derivative of the Voigt function may be simplified using the chain rule:
\frac{dU(p,q)}{dt} = \frac{dU(p,q)}{dp}\frac{dp}{dt} = \frac{dU(p,q)}{dp} \frac{\sigma_f}{\sigma_t f_0}
Thus, Eq. \ref{eq:conv_2} becomes
s * r = \\
\frac{R_0}{2\pi f_0}\left(s(t) + E_0 \sigma_t \left(\frac{\sigma_f}{f_0}\right) e^{-\frac{1}{2}\left(\frac{t}{\sigma_t}\right)^2} \frac{d}{dp}\right)U(p,q) \label{eq:conv_3}
The envelope of Eq. \ref{eq:conv_3} can be computed numerically, which represents an alternative approach to that represented by Eq. \ref{eq:awesome}.

>>>>

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
%\usepackage{empheq}
\usepackage{verbatim}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

@@

@@

The remaining integral is the Laplace transform of the shifted Dawson function, $\mathcal{L}\lbrace D(u-x)\rbrace_k$.  The final result is
r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right) \label{eq:Im_result}
Though a closed analytic form for $\mathcal{L}\lbrace D(u-x)\rbrace_k$ is elusive, finishing this calculation through numerical integration is straightforward.
\item Combining Eq. \ref{eq:Re_result} and Eq. \ref{eq:Im_result} gives $r_a(t) * s_a(t)$, since
r_a(t) * s_a(t) = r_a(t) * \Re\lbrace s_a(t)\rbrace + j r_a(t) * \Im\lbrace s_a(t)\rbrace
which yields

@@

r_a(t) * s_a(t) = \\ -\sqrt{\pi} R_0 E_0 \sigma_t^2 \left(x e^{-x^2} w(q) + \left(\frac{j}{2}\right) e^{-x^2} \frac{dw(q)}{dq} \right) + \\ \frac{2j}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\mathcal{L}\lbrace D(u-x)\rbrace_k\right) \label{eq:final}

@@

The units of convolution should be $R_0 E_0\sigma_t^2$, and each term in Eq. \ref{eq:final} has these units.  Remember that the relationship between $q$ and $x$ is given by

@@

q = -jb = -j\left(x + \frac{z}{2}\right) \\

@@

Taking the magnitude of Eq. \ref{eq:final}, and multiplying by $1/2$, yields the \textbf{Hilbert envelope of the convolution of $s(t)$ with $r(t)$:}

@@

\clearpage
\item It is important to note that the convolution of $s(t)$ and $r(t)$ may be done analytically in the time-domain:
s * r = \int_{-\infty}^{\infty} s(t-\tau) r(\tau) d\tau 
Inserting the definitions of $s(t)$ and $r(t)$,
s * r = \\ -E_0 R_0 \int_{-\infty}^{\infty} (t-\tau) e^{-\frac{1}{2}\left(\frac{t-\tau}{\sigma_t}\right)^2} \Re\left\lbrace e^{2\pi j f_0 \tau} e^{-2\pi\gamma \tau} \right\rbrace u(\tau) d\tau
Using the previous definitions of $x$, $y$, and $z$ gives
s * r = -2R_0 E_0 \sigma_t^2 \int_{0}^{\infty} (x-y) e^{-(x-y)^2} \Re\left\lbrace e^{zy} \right\rbrace dy
Note that the $\Re\lbrace \rbrace$ operator can encompass the whole integral, since $s(t)$ is real.  Splitting the integral and employing differentiation under the equals sign yields
s * r = \\ -2R_0 E_0 \sigma_t^2 \Re\left\lbrace xe^{-x^2}I(x,z) - \frac{1}{2}e^{-x^2} \frac{dI(x,z)}{dx} \right\rbrace \label{eq:conv_sr}
with
I(x,z) = \int_0^{\infty} e^{-y^2 + (2x + z)y}dy
Let $b=x+\frac{1}{2}z$, and $a = -jb$.  Completing the square in the exponent of $I(x,z)$ gives
I(x,z) = \frac{\sqrt{\pi}}{2} w(a)
where $w(a)$ is the Faddeeva function.  Note that the Faddeeva function is \textit{entire}, meaning the $\Re\lbrace \rbrace$ operator and differentiation commute.  Inserting this result into Eq. \ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives
s * r = \\ -\sqrt{\pi}R_0 E_0 \sigma_t^2 \left(xe^{-x^2} \Re\left\lbrace w(a)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(a)\rbrace}{dx} \right)
The Faddeeva function may be split into real and imaginary parts via the \textit{Voigt functions}:

@@

w(a) &= U(p,q) + jV(p,q) \\
p &= 

@@
